---
title: "Sailershausen B1-B2 Species Sensitivity Analysis"
format: html
server: shiny
toc: true
---

```{r}
#| label: Setup
#| context: setup
#| echo: false
#| message: false
#| warning: false
source("External/Vs.R")
source("External/custom_functions.R")  #Load your new functions

library(VSLiteR)
library(dplR)
library(ggplot2)
library(tidyverse)
library(shiny)
library(bslib)
library(DT)
```

```{r}
#| echo: false
#| context: data
#| message: false
#| warning: false

# Load tree ring data
tree_data <- list(
  b1ac = read.rwl("Data/b1ac.rwl"),
  b1apl = read.rwl("Data/b1apl.rwl"),
  b1aps = read.rwl("Data/b1aps.rwl"),
  b1fs = read.rwl("Data/b1fs.rwl"),
  b1pa = read.rwl("Data/b1pa.rwl"),
  b1qp = read.rwl("Data/b1qp.rwl"),
  b2ac = read.rwl("Data/b2ac.rwl"),
  b2pa = read.rwl("Data/b2pa.rwl"),
  b2qp = read.rwl("Data/b2qp.rwl")
)

# Load climate data
climate_b1 <- read_csv2("Data/B1_Sailerhausen.csv")
climate_b2 <- read_csv2("Data/B2_Sailerhausen.csv")
cordex_b1 <- read_csv2("Data/cordex_b1_padded.csv")
cordex_b2 <- read_csv2("Data/cordex_b2_padded.csv")

# Detrend all datasets
tree_detrended <- lapply(tree_data, detrend, method = "Spline", nyrs = 32)

# Create chronologies
tree_chron <- lapply(tree_detrended, chron)

# Estimate parameters for all species
params <- list(
  b1ac = estimate_parameters(tree_chron$b1ac, climate_b1),
  b1apl = estimate_parameters(tree_chron$b1apl, climate_b1),
  b1aps = estimate_parameters(tree_chron$b1aps, climate_b1),
  b1fs = estimate_parameters(tree_chron$b1fs, climate_b1),
  b1pa = estimate_parameters(tree_chron$b1pa, climate_b1),
  b1qp = estimate_parameters(tree_chron$b1qp, climate_b1),
  b2ac = estimate_parameters(tree_chron$b2ac, climate_b2),
  b2pa = estimate_parameters(tree_chron$b2pa, climate_b2),
  b2qp = estimate_parameters(tree_chron$b2qp, climate_b2)
)
```

## B1ac - Acer campestre

```{r}
sliderInput("T1_b1ac", "T1", min = 0, max = 8.5, value = params$b1ac[1])
sliderInput("T2_b1ac", "T2", min = 9, max = 20, value = params$b1ac[2])
sliderInput("M1_b1ac", "M1", min = 0.01, max = 0.03, value = params$b1ac[3])
sliderInput("M2_b1ac", "M2", min = 0.1, max = 0.5, value = params$b1ac[4])
selectInput("rcp_b1ac", "Scenario", choices = c("RCP_85", "RCP_45", "RCP_26"))
selectInput("rcm_b1ac", "Regional Climate Model", 
            choices = c("CLMcom-CCLM4-8-17", "KNMI-RACMO22E", "SMHI-RCA4", 
                       "CEC-WETTREG2018", "UHOH-WRF361H"))

plotOutput("b1ac_rcp_plot")
plotOutput("b1ac_rcm_plot")
```

```{r}
#| context: server

# Generic function to render plots for any species
render_species_plot <- function(species_id, chrono, climate_hist, climate_proj, 
                               filter_var, input_param_prefix, input_filter) {
  renderPlot({
    # Get adjusted parameters from sliders
    params_adj <- c(
      T1 = input[[paste0("T1_", species_id)]],
      T2 = input[[paste0("T2_", species_id)]],
      M1 = input[[paste0("M1_", species_id)]],
      M2 = input[[paste0("M2_", species_id)]]
    )
    
    # Run forward models
    hist_forward <- forward_historic(params_adj, climate_hist)
    proj_forward <- run_projection(params_adj, climate_proj, 
                                   filter_var, input[[input_filter]])
    
    # Create combined data and plot
    combined <- create_combined_data(chrono, hist_forward, proj_forward)
    plot_sensitivity(combined)
  })
}
